#Almond Yield Sensitivity 

```{r warning = FALSE, message = FALSE}
#Load libraries
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

library(purrr)

library(ggpubr)
```


##Call the almond profit model
```{r}
source("profit_model.R")
calculate_almond_profit

clim <- read.table("clim.txt" , header = TRUE)
```

##Do a simple informal sensitivity analysis of almond yield profit using at least 2 parameters
```{r}
cost_per_hectare = rnorm(mean = 100, sd = 5, n = 20) #creating a normal distribution
sensi_almond = cost_per_hectare %>% map(~calculate_almond_profit(cost_per_hectare = .x, price_per_kg = 200, year = 2024)) 

# Create a dataframe of just annual data
tmp = map_df(sensi_almond,`[`, c("annual")) 

almonddf = data.frame(year = tmp$annual$year, profit= tmp$annual$elect) #need to update this with relevant details for profit calc

```

##Create 2 graphs of the results - you can decide what is the most meaningful graph 

```{r}
#Plotting the mean annual plot varies by cost per hectare
site2[[1]]

tmp = map_df(site2,`[`, c("mean")) 

site2_mean = data.frame(cost_per_hectare = cost_per_hectare, profit= tmp)
ggplot(site2_mean, aes(y=mean))+geom_boxplot()+
  labs(x="Cost per Hectare ($)")

```

```{r}
#Comparing relationship of cost to profit
ggplot(site2_mean, aes(cost_per_hectare, mean))+geom_point()+
  labs(y="Cost per Hectare ($)", x="Profit ($)")
```


##Results
Write a short paragraph (in the Rmarkdown document) to summarize interpretation of your model results (e.g what do 'take away' from your model and sensitivity analysis)

